---
title: "visualization"
author: "Kai Ye"
date: "2/21/2023"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The pre_work before the visualization.
train_data_nomissing is the raw data without missing(all number)
train_data_redo is the data change the lable data to its label


```{r}
library(ggplot2)
library(readr)

data <- read.csv("data/detailed.cleveland.data.csv")
test_train_split <- sample(c(FALSE,TRUE), nrow(data), replace=TRUE, prob = c(0.2, 0.8))



test_data <- data[!test_train_split,]
train_data <- data[test_train_split,]

summary(train_data)
train_data$CA = as.numeric(train_data$CA)
train_data$Thal = as.numeric(train_data$Thal)# Notice when we read the CA from the csv, the CA will be read as character but it should be as numerical. See the summary
summary(train_data)
head(train_data)
train_data[train_data == "?"] = NA
which (is.na(train_data),arr.ind=TRUE)
train_data_nomissing = na.exclude(train_data) 
train_data_redo = train_data_nomissing

train_data_redo$Outcome[which(train_data_redo$Outcome == 1)] = "Have heart disease of type 1"
train_data_redo$Outcome[which(train_data_redo$Outcome == 2)] = "Have heart disease of type 2"
train_data_redo$Outcome[which(train_data_redo$Outcome == 3)] = "Have heart disease of type 3"
train_data_redo$Outcome[which(train_data_redo$Outcome == 4)] = "Have heart disease of type 4"
train_data_redo$Outcome[which(train_data_redo$Outcome==0)] = "Do not have heart disease"

train_data_redo$Sex[which(train_data_redo$Sex==0)] = "Female"
train_data_redo$Sex[which(train_data_redo$Sex==1)] = "Male"

train_data_redo$CP[which(train_data_redo$CP==1)] = "Typical angina"
train_data_redo$CP[which(train_data_redo$CP==2)] = "Atypical angina"
train_data_redo$CP[which(train_data_redo$CP==3)] = "Non-anginal pain"
train_data_redo$CP[which(train_data_redo$CP==4)] = "Asymptomatic"

train_data_redo$FBS[which(train_data_redo$FBS==0)] = "Fasting blood sugar <= 120 mg/dl"
train_data_redo$FBS[which(train_data_redo$FBS==1)] = "Fasting blood sugar > 120 mg/dl"

train_data_redo$RestECG[which(train_data_redo$RestEC==0)] ="Normal"
train_data_redo$RestECG[which(train_data_redo$RestEC==1)] ="Having ST-T wave abnormality"
train_data_redo$RestECG[which(train_data_redo$RestECG==2)] ="Showing probable or definite left ventricular hypertrophy"

train_data_redo$Exang[which(train_data_redo$Exang==0)] = "No"
train_data_redo$Exang[which(train_data_redo$Exang==1)] = "Yes"

train_data_redo$Slope[which(train_data_redo$Slope==1)] ="Upsloping"
train_data_redo$Slope[which(train_data_redo$Slope==2)] ="Flat"
train_data_redo$Slope[which(train_data_redo$Slope==3)] ="Downsloping"
  
  



train_data_redo$Thal[which(train_data_redo$Thal==3)] ="Normal"
train_data_redo$Thal[which(train_data_redo$Thal==6)] ="Fixed defect"
train_data_redo$Thal[which(train_data_redo$Thal==7)] ="Reversable defect"
features_continuous=train_data_nomissing[,c("Age", "Trestbps", "Chol", "Thalach", "OldPeak","Outcome")]
outcome_variable = train_data_redo$Outcome
features_continuous=data.frame(features_continuous,outcome_variable)
```
##the visualization for the distrubution

```{r cars}

for (i in colnames(train_data_redo)) {
  if (i!="Trestbps"&i!="Chol"&i!="Thalach"&i!="OldPeak"&i!="Age"&i!="Outcome") {
    print(i)
    print(ggplot(train_data_redo, aes(!!sym(i))) + geom_bar(aes(fill = Outcome), 
                                                 ) +scale_fill_manual(values = c("#FFFF00", "#00BBFF","#9999FF","#0000FF","#5500FF"))+ ggtitle(paste("Histogram of",i)) + xlab(i))
    
  }
  else if (i == "Chol"){
          print(ggplot(train_data_redo, aes(!!sym(i))) + geom_histogram(aes(fill = Outcome), 
bins = 100                                               ) +scale_fill_manual(values = c("#FFFF00", "#00BBFF","#9999FF","#0000FF","#5500FF"))+ ggtitle(paste("Histogram of",i)) + xlab(i))
    } else if (i == "OldPeak"){
          print(ggplot(train_data_redo, aes(!!sym(i))) + geom_histogram(aes(fill = Outcome),
bins = 50                          ) + scale_fill_manual(values = c("#FFFF00", "#00BBFF","#9999FF","#0000FF","#5500FF"))+ggtitle(paste("Histogram of",i)) + xlab(i))
    }
    else {
    if (i!="Outcome") {
          print(ggplot(train_data_redo, aes(!!sym(i))) + geom_histogram(aes(fill = Outcome), 
binwidth = 1                                                ) + scale_fill_manual(values = c("#FFFF00", "#00BBFF","#9999FF","#0000FF","#5500FF"))+ggtitle(paste("Histogram of",i)) + xlab(i))
    }
    
  }
    
}




```
## the visualization about continuous variable.
```{r}
library(GGally)

p = ggpairs(features_continuous,columns=c(1:6),mapping=ggplot2::aes(colour=outcome_variable))
#maybe in r the index will be strange, but when save as png it will be ok


ggsave("p.png",width = 20,height = 10)
p

```
## the visualization about the corr between different features(notice i just use the number in the data set to get a overview, maybe we can do it more correct, if have time.)
```{r}
library(corrplot)
library(ggplot2)
library(ggcorrplot)
library(vcd)
library(psych)
library(ggrepel)
 
cor(train_data_nomissing)
corr=cor(train_data_nomissing[,-14],method="spearman")
corrp=ggcorrplot(corr, lab =T, lab_size = 4) 
#maybe in r 4 will be big, but when save as png it will be ok
ggsave("corrp.png",width = 20,height = 10)
corrp

```





